Complete representability for canonical extensions of representable cylindric algebras

### 2021-11-10 cylindric-notes/Text.tex
updates in cylindric notes

\author{Daniel Rogozin}
\date{}
\title{Representable cylindric algebras of dimension $\omega$}

@@

Suppose $\mathcal{C} \in {\bf RCA}_{\omega}$, whether $\mathcal{C}^{+}$ has a complete, $\omega$-dimensional representation? \cite{hirsch2002relation}

@@

\begin{defin}
 A cylindic set algebra of dimension $\alpha$ is an algebra consisting of a set $S$ of $\alpha$-ry relation on some base set $U$
   with the constants and operations $0 = \emptyset$, $1 = \prescript{\alpha}{}U$, $\cap$, $-$, the diagonal elements $(D_{ij})_{i, j < \alpha}$, the cylindrifications $(C_i)_{i < \alpha}$. A generalised cylindric set algebra of dimension $\alpha$ is a subdirect of cylindric algebras that have dimension $\alpha$.
\end{defin}

@@

@@

\begin{lemma}
${\bf RCA}_{\omega} = {\bf S} \: \mathfrak{Cm} {\bf Ud} \mathcal{F} \mathfrak{ct}_{\alpha}$
\end{lemma}

>>>>

\author{Daniel Rogozin}
\date{}
\title{Complete representability for canonical extensions of representable cylindric algebras}

@@

Given $\mathcal{C} \in {\bf RCA}_{\omega}$, whether $\mathcal{C}^{+}$ has a complete, $\omega$-dimensional representation? \cite{hirsch2002relation}

@@

\begin{defin}
 A cylindic set algebra of dimension $\alpha$ is an algebra consisting of a set $S$ of $\alpha$-ry relation on some base set $U$
   with the constants and operations $0 = \emptyset$, $1 = \prescript{\alpha}{}U$, $\cap$, $-$, the diagonal elements $(D_{ij})_{i, j < \alpha}$, the cylindrifications $(C_i)_{i < \alpha}$. A generalised cylindric set algebra of dimension $\alpha$ is a subdirect of cylindric algebras that have dimension $\alpha$.
   ${\bf Cs}_{\alpha}$ denotes the class of all cylindric set algebras of dimension $\alpha$.
\end{defin}

@@

We are interested in the special case of cylindric $\omega$-frames called Cartesian structure of dimension $\omega$. To be more precise:

\begin{defin}
Let $U$ be a set and $V \subseteq \prescript{\omega}{}U$ be a non-empty subset of the full Cartesian space of dimension $\omega$, then an $\alpha$-dimension Cartesian structure generated by $V$ is an $\omega$-frame $\mathfrak{G}(V) = \langle V, (R_{i})_{i < \omega}, (E_{ij})_{i, j < \omega} \rangle$ such that:
\begin{enumerate}
\item $R_i = \{ (w, v) \: | \: w, v \in V, w_k = w_k, k < \omega, i \neq k \}$
\item $E_{ij} = \{ w \in V \: | \: w_i = w_j \}$
\end{enumerate}
$\mathfrak{G}(\prescript{\omega}{}U)$ is the full $\omega$-dimensional Cartesian structure. $\mathcal{F} \mathfrak{c}\mathfrak{t}_{\omega}$ is the class of all full $\omega$-dimensional Cartesian structures.
\end{defin}

Every cylindric set algebra is a subalgebra of some complex algebra induced by an $\omega$-dimensional Cartesian structure. That is, we have the following characterisation:

\begin{lemma}
${\bf I}{\bf Cs}_{\omega} = {\bf S} \mathfrak{Cm} \mathcal{F} \mathfrak{c}\mathfrak{t}_{\omega}$.
\end{lemma}

@@

\begin{lemma}
${\bf RCA}_{\omega} = {\bf S} \: \mathfrak{Cm} {\bf Ud} \mathcal{F} \mathfrak{ct}_{\omega}$
\end{lemma}
